On the Dynamics of Anthropomorphism in Robotics

### 2014-01-21 dynamics-anthropomorphism.tex
Wrapped lines to 80 chars

\abstract{While anthropomorphism in robotics is a commonly discussed trait of
HRI, it paradoxically lacks formal grounds. This article
attempts first at providing a comprehensive synthesis of the social
phenomenon of \textit{perceiving human-like characteristics in non-human
agents and attributing those characteristics to robots}. We draw on
social sciences and psychology, as well as on a critical survey of
existing literature in the HRI community, to ground the concept of
\textit{anthropomorphism}. Supported by extensive literature review
and long-term field studies, we suggest to go beyond the traditional
perception of anthropomorphism as a static feature of a system: we propose to
understand anthropomorphism as a dynamic, non-monotonic and context-dependent
process, which evolves over time and accounts for special events such as the
so-called \textit{novelty effect}. To this end, we introduce a model of
anthropomorphism that analyzes the phenomenon along three interaction phases,
and we discuss cognitive interpretations that follow.

@@

%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
% We would further like to review and discuss research on anthropomorphism in robotics and human-like design of robots. We first provide a comprehensive understanding of the phenomenon drawing on theories from developmental psychology and cognitive sciences. We then present the trends of different kinds of anthropomorphic forms in robots and discuss their role in social robotics. The article integrates related work from human-robot interaction studies, reporting on findings from experiments with human subjects interacting with and evaluating various types of systems. We try to give a coherent view on the topic, outline similarities and antithetic findings, and contribute to a better understanding of anthropomorphism in robotics, and the acceptance of human-like characteristics in robots. We also aim to constructively discuss anthropomorphic design of personal and socially interactive robots.

@@

\begin{figure}[ht!]\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
% figure caption is below the figure
 \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
 \label{fig:anthropomorphism_and_interaction}       % Give a unique label
 \end{figure}

@@

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.6]{uncanny-valley.jpg}
% figure caption is below the figure
 \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
 \label{fig:uncanny_valley}       % Give a unique label
 \end{figure}

@@

\begin{description}
	\item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot is impacted by the context of use and purpose of the robot. A social context and purpose of the robot increases anthropomorphism. \textit{(context and purpose of the robot)}
\end{description}

@@

We would like to acknowledge here the fruitful discussions with A Jung Moon and
Aude Billard.\\

>>>>

\abstract{While anthropomorphism in robotics is a commonly discussed trait of
HRI, it paradoxically lacks formal grounds. This article
attempts first at providing a comprehensive synthesis of the social
phenomenon of \textit{perceiving human-like characteristics in non-human
agents and attributing those characteristics to robots}. We draw on
social sciences and psychology, as well as on a critical survey of
existing literature in the HRI community, to ground the concept of
\textit{anthropomorphism}. Supported by extensive literature review
and long-term field studies, we suggest to go beyond the traditional
perception of anthropomorphism as a static feature of a system: we propose to
understand anthropomorphism as a dynamic, non-monotonic and context-dependent
process, which evolves over time and accounts for special events such as the
so-called \textit{novelty effect}. To this end, we introduce a model of
anthropomorphism that analyzes the phenomenon along three interaction phases,
and we discuss cognitive interpretations that follow.
}

@@

%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
% We would further like to review and discuss research on anthropomorphism in
% robotics and human-like design of robots. We first provide a comprehensive
% understanding of the phenomenon drawing on theories from developmental
% psychology and cognitive sciences. We then present the trends of different
% kinds of anthropomorphic forms in robots and discuss their role in social
% robotics. The article integrates related work from human-robot interaction
% studies, reporting on findings from experiments with human subjects
% interacting with and evaluating various types of systems. We try to give a
% coherent view on the topic, outline similarities and antithetic findings, and
% contribute to a better understanding of anthropomorphism in robotics, and the
% acceptance of human-like characteristics in robots. We also aim to
% constructively discuss anthropomorphic design of personal and socially
% interactive robots.

@@

\begin{figure}[ht!]\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
% figure caption is below the figure
 \caption{Anthropomorphism emerges in the (real or imagined) interaction between
 robot and user; illustration taken from \cite{persson_anthropomorphism_2000}
 \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}

 \label{fig:anthropomorphism_and_interaction}       % Give a unique label
 \end{figure}

@@

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.6]{uncanny-valley.jpg}
% figure caption is below the figure
 \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally
 from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}

 \label{fig:uncanny_valley}       % Give a unique label
 \end{figure}

@@

\begin{description}
    \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
        is impacted by the context of use and purpose of the robot. A social
        context and purpose of the robot increases anthropomorphism.
        \textit{(context and purpose of the robot)}

\end{description}

@@

We would like to acknowledge here the fruitful discussions with A Jung Moon and
Aude Billard.
